Response to the defense feedback

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new cryptographic algorithms (e.g., ChaCha20) that are resilient to cache side-channel attacks.

>>>>

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks. Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.  Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which compasses formal verification methods to design, analyze and implement the cryptography libraries. Formal verification on side-channel leakages start with a leakage model, which abstract what an attacker can observe during an attack.
